\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{hyperref}

\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 160mm
\textheight 200mm

\pagestyle {plain}
\pagenumbering{arabic}

\newcounter{stepnum}

\title{Greedy Algorithm Drasil Case Study}
\author{Don Chen}
\date{\today}

\begin {document}

\tableofcontents

\section{Reference Material}

This section records information for easy reference.

\section{Problem Description}
In the real world, we are facing a lot of optimization problem. For example:
A saleman would like to travel all the cities in the Great Toronto Area to promote companies products.
This person does not want to visit the city two times. What is the shortest possible route that visits 
each city exactly once? This problem can also apply to logistics and telecommunication.
Find the most optimized solution usually will bring the cost down.

\section{General System Description}
This section provides general information about the system including identifying the interfaces between the system 
and its environment (system context), describing the user characteristics and listing the system constraints.

\section{Specific System Description}
This section first presents the problem description, which gives a high-level view of the problem to be solved. 
This is followed by the solution characteristics specification, which presents the assumptions, theories, theoretical 
models, general definitions, data definitions, and finally the instance models that model the weighted graph.

\subsection{General Definition}

\begin{itemize}
    \item Vertice: a basic unit(such a city) disperse in a graph.
    \item Edge: a connction bewteen two vertices.
    \item Graph: A graph G is an ordered triple (V(G), E(G), f) consisting of a nonempty set V(G) of vertices, 
    a set E(G) of edges, and an incidence function f that associates with each edge and two vertices.
    \item function f: If e is an edge and u and v are vertices, 
    u, v $\in$  V (G), such that f(e) = uv, then e is said to join u and v; u and v are endpoints of edge e.     
    \item Weight: With each edge e of G let there be associated a real number w(e).
    \item Weighted Graph: A weighted graph is a graph with each edge e of G let there be associated a real number w(e).
\end{itemize}

% \subsection{Example}
% \begin{itemize}
%     \item G = (V(G), E(G), f, w)
%     \item V(G) = {$v_1$, $v_2$, $v_3$, $v_4$, $v_5$}
%     \item E(G) = {$e_1$, $e_2$, $e_3$, $e_4$, $e_5$, $e_6$, $e_7$, $e_8$}
%     \item f($e_1$) = $v_1v_2$, f($e_2$) = $v_2v_3$, f(e3) = $v_3v_3$, f(e4) = $v_3v_4$, 
%     \item f(e5) = $v_2v_4$, f($e_6$) = $v_4v_5$, f($e_7$) = $v_2v_5$, f($e_8$) = $v_2v_5$
%     \item w($e_1$) = $n_1$, w($e_2$) = $n_2$, w($e_3$) = $n_3$, w($e_4$) = $n_4$,
%     \item w($e_5$) = $n_5$, w($e_6$) = $n_6$, w($e_7$) = $n_7$, w($e_8$) = $n_8$
% \end{itemize}

\subsection{Goal Statements}
\begin{itemize}
    \item General: Find the shortest possible route that visits each city exactly once.
    \item Mathematical Definition: In the weighted graph, find the shorest path which contains all vertices.
\end{itemize}

\subsection{Assumptions}
\begin{itemize}
    \item V and E are finite sets.
    \item It is undirected graphs, means f(e) = uv = vu.
    \item It is a connected graph.
    \item There is no loop in the graph.
\end{itemize}

\subsection{Theoretical Model}
min$\sum$\{W\}, both of its edges $e_1$, $e_2$, $...$, $e_k$ and its vertices $v_0$, $v_1$, $...$ , $v_k$ are distinct
W = {$v_0$, $e_1$, $v_1$, $...$, $e_k$, $v_k$} 
The Shorest Path: a path has the smallest number of sum of its edges' weight.

\subsection{Supporting Data Definitions}
\begin{itemize}
    \item Finite Graph: A graph is finite if both its vertex set and edge set are finite.
    \item Endpoint: if f(e) = uv, edge e has endpints of u and v. u and v $\in$  V(G).
    \item Loop: An edge with identical ends. f(e) = vu and v = u. u and v $\in$  V(G).
    \item Connected Graph: if for every u, v $\in$  V(G) there exists f(e) = uv. Otherwise G is called disconnected.
    \item Walk: A walk is a sequence W = {$v_0$, $e_1$, $v_1$, $...$, $e_k$, $v_k$}, whose terms are alternatively vertices 
    and edges such that for 1$\le$i$\le$k, the edge $e_i$ has endpoints $v_{i-1}$ and $v_i$. f($e_i$) = $v_{i-1}v_i$. k is the length of W.
    \item Trail: If the edges $e_1$, $e_2$, $...$, $e_k$ of a walk are distinct.
    \item Path: a path is a walk if both of its edges $e_1$, $e_2$, $...$, $e_k$ and its vertices $v_0$, $v_1$, $...$ , $v_k$ are distinct.
    \item Closed: A u,v-walk has first vertex u and last vertex v. 
    When the first and last vertex of a walk, trail or path are the same, we say that they are closed. 
\end{itemize}

\subsection{Instance Models}
\begin{itemize}
    \item Input: G = (V(G), E(G), f, w)
    \item Output: a sequence
\end{itemize}

\section{Algorithm}
\begin{itemize}
    \item Kruskal’s Algorithm
    \item Kruskal-Abstract(G = (V, E), w) 
    \item initialize F = (V, $\oslash$)
    \item for edges e in increasing order of length w
    \item \{if edges e are do not form a cycle with F
    \item add uv to F\}
    \item return F

    \item Nearest Neighbor Alorithm(usually can't find an optimized solution)
\end{itemize}

\section{Question}
\begin{itemize}
    \item clarify on Walk, how the sequence formed? V and G are set in the definition.
    \item remove the conditon of "returns to the origin city"
\end{itemize}

\section{Reference}
\begin{itemize}
    \item Graph Theory With Applications by J.A. Bondy and U. S. R. Murty
    \item \href{http://math.mit.edu/~goemans/18433S15/TSP-CookCPS.pdf}{Nearest Neighbor Alorithm} 
    \item \href{https://www.ams.org/journals/proc/1956-007-01/S0002-9939-1956-0078686-7/home.html}{Kruskal  Alorithm in TSP} 
\end{itemize}

\end {document}