%-------------------------
% Resume in Latex
% Author : Dong Chen
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Dong Chen} \\ \vspace{1pt}
  \small +86-15680477765 $|$ \href{mailto:info@donchen.page}{\underline{info@donchen.page}} $|$ 
  \href{https://www.linkedin.com/in/dcengr}{\underline{linkedin.com/in/dcengr}} $|$
  \href{https://www.donchen.page}{\underline{www.donchen.page}}
\end{center}


%-----------Professional Profile and Objective-----------
\section{Professional Profile and Objective}
Motivated and driven software engineer is seeking opportunities to obtain experience and competencies 
through research in the areas of machine learning and data analytics. 
An experienced agile professional with depth of knowledge in the software development, engineering, 
mobile development, and object-oriented programming.


%-----------Education-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University, College of Engineering, Hamilton, ON, Canada}
      {Master of Engineering in Software Engineering}{Jan 2021 -- Present}
    \resumeSubheading
      {Boston University, College of Engineering, Boston, MA, USA}
      {Master of Engineering in Systems Engineering - GPA:\textbf{3.35}/4.00}{Graduation Date: May 2016}
    \resumeSubheading
      {University of Iowa, College of Engineering, Iowa City, IA, USA}
      {Bachelor of Science in Industrial Engineering - GPA:3.23/4.00}{Graduation Date: May 2014}
  \resumeSubHeadingListEnd


%-----------Work Experience-----------
\section{Work Experience}
\resumeSubHeadingListStart
  \resumeSubheading
  {\textbf{Software Engineer} with CentralSquare Technologies, Sioux Fall, SD, USA}{Oct 2018 – Oct 2019}
    \resumeItemListStart
      \resumeItem{Maintained a flagship product, Pro Suite, that cover 274 million population across North America 
      in public safety industries.}
      \resumeItem{Tested development methodology in an agile environment and provided recommendations 
      for continuous improvement.}
      \resumeItem{Implemented and added new features in complex software system based on customer’s feedbacks, 
      requests and capacity, and led to reach over 95\% positive customer reviews.}
      \resumeItem{Increased program’s flexibility by building class definition in the database, 
      led to 100\% compatibility with existing functions and 30\% reduction in support tickets.}
    \resumeItemListEnd


% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


  \resumeSubSubheading
  {\textbf{Software Developer} with B2BGateway.Net, Hope Valley, RI, USA}{Aug 2016 – Sep 2018}
    \resumeItemListStart
      \resumeItem{Collaborated with multiple teams daily to publish online warehouse management tools for 
      multimillion documents processed each year along with technology such as model, view and controller technique.}
      \resumeItem{Designed aesthetic, well-maintained and mobile-friendly web pages by implementing web technologies,
      such as AngularJS}
      \resumeItem{Published an online parking reservation application in mobile platforms for clients across US.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%{\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%\resumeItemListStart
%-----------Engineering Project Experience-----------
\section{Engineering Project Experience}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Graph Theory Network Architecture Design}}{Jan 2016 – May 2016}
    \resumeItemListStart
      \resumeItem{Developed a geographical mapping application that applied the Dijkstra algorithm and Yen algorithm 
      to find the shortest path along with the next top three alternative shortest paths.}
      \resumeItem{Optimized app’s performance and determined extreme cases, such as a dead end can crash the app.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{Machine Learning Practice} – Decision Tree, Boosted Decision Tree, Random Forest}{Jan 2016 – May 2016}
    \resumeItemListStart
      \resumeItem{Designed three different models that advanced from basic to complex, continually observed 
      difference between perdition accuracy, and provided further solution to improve each model.}
      \resumeItem{Predicted wine quality and reached 70\% accuracy in over 100,000 wine quality data 
      using Random Forest technique.}
      \resumeItem{Implemented Random Forest and Boosted Decision Tree, used cross validation to select 
      the best minimum observation per leaf and desired number of trees generated.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Scholarships and Volunteer-----------
\section{Scholarships and Volunteer}
\resumeSubHeadingListStart
  \resumeSubheading
  {University of Iowa National Scholar Award}{Aug 2010 – May 2014}
  \resumeSubheading
  {Alpha Pi Mu Industrial Engineering Honor Society – Award Coordinator}{Jan 2012 – Jan 2014}
  \resumeSubheading
  {FTC Iowa Technology Championship – Volunteer Manager}{FEB 2012}
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}